\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-26 doc/paper.tex
Intro. Fixes #114, fixes #115, fixes #116, fixes #117, fixes #118, fixes #119, fixes #120.

	However, this ubiquity is not without danger: as more people adopt these tools
	and make larger and more complex sheets, the cost of failure grows too. To
	stress this, the European Spreadsheet Risks Interest Group (EuSpRIG) documents
	many horror stories of spreadsheets gone terribly
	wrong\footnote{http://www.eusprig.org/horror-stories.htm}. One such story tells
	of a 2013 economics paper which drew stark connections between debt and
	national growth. Its findings shaped many political initiatives throughout the
	United States and Europe. However, other researchers soon discovered that a
	critical coding error in the research spreadsheets hampered the results and
	that, by correcting this error, they completely reversed the findings! And this
	is only one of several accounts; even if most spreadsheet errors are relatively
	benign, poor spreadsheet practice can risk millions, if not billions, of
	dollars \cite{powell2009impact}.

	From these stories, we can see the dire importance of understanding how people
	actually use spreadsheets, if only to avoid disasters. Fortunately, spreadsheet
	researchers have supported this by amassing spreadsheet collections from
	diverse sources, industrial to academic. Collections like EUSES
	\cite{fisher2005euses}, Fuse \cite{barik2015fuse}, and the Enron corpus
	\cite{hermans2015enron} have already fueled productive research across the
	field, such as in Hermans' \cite{hermans2012detecting} or Jansen's
	\cite{jansen2015code} search for code smells\footnote{Or, instances of
		inelegant code that do not necessarily cause problems alone but nevertheless
		suggest a need for refactoring to prevent future problems. More on this in
		section IV.} in spreadsheet environments or Aivaloglou and colleague's work on
	making a grammar to capture every possible spreadsheet program in Excel
	\cite{aivaloglou2015grammar}. Additionally, some research has focused simply on
	comparing these collections, as Jansen did in 2015, to discover variation in
	spreadsheet techniques over time and location \cite{jansen2015enron}.

	Considering the sheer value of spreadsheets and all of these resources to
	describe their use, it becomes necessary that we design tools to make sense of
	it all. Tools, then, that empower people to explore datasets are rife with the
	potential to improve the current design of spreadsheets themselves and educate
	new generations of spreadsheets users on how to work best.

>>>>

	However, this ubiquity is not without danger: as more people adopt these tools
	and make larger and more complex sheets, the cost of failure grows too. For examples
	of this, the European Spreadsheet Risks Interest Group (EuSpRIG) documents
	many horror stories of spreadsheets gone 
	wrong\footnote{http://www.eusprig.org/horror-stories.htm}. One such story tells
	of a 2013 economics paper which drew connections between debt and
	national growth. Its findings shaped many political initiatives throughout the
	United States and Europe. However, other researchers soon discovered that a
	critical selection error in the research spreadsheets hampered the results and
	that, by correcting this error, the findings reversed completely! And this
	is only one of several accounts; even if most spreadsheet errors are relatively
	benign, poor spreadsheet practice can risk millions, if not billions, of
	dollars \cite{powell2009impact}.

	From these stories, we can see the dire importance of understanding how people
	actually use spreadsheets, if only to avoid disasters. Fortunately, spreadsheet
	researchers have supported this by amassing spreadsheet collections from
	diverse sources, industrial to academic. Collections like EUSES
	\cite{fisher2005euses}, Fuse \cite{barik2015fuse}, and the Enron corpus
	\cite{hermans2015enron} have already fueled productive research across the
	field, such as in Hermans' \cite{hermans2012detecting} and Jansen's
	\cite{jansen2015code} search for code smells in spreadsheet environments or
	Aivaloglou and colleague's work on making a grammar to capture every possible
	spreadsheet program in Excel \cite{aivaloglou2015grammar}. Additionally, some
	research has focused on comparing these collections, as Jansen did in
	2015, to discover variation in spreadsheet techniques over time and location
	\cite{jansen2015enron}.

	Considering the value of spreadsheets and all of these resources to
	describe their use, it becomes necessary that we design tools to make sense of
	it all. Tools, then, that empower people to explore datasets are rife with the
	potential to improve the current design of spreadsheets themselves and educate
	new generations of spreadsheets users on how to work best.
